---
title: "Cabbages"
author: "Anthony Falconio"
date: "Fall 2023"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
library(ggplot2)

# Create a ggplot boxplot with light blue boxes
ggplot(veggy, aes(x = Cult, y = VitC)) +
  geom_boxplot(fill = "lightblue", notch = TRUE, outlier.colour = "red") +  # Set box fill color to light blue, notch to TRUE, and outlier color to red
  labs(x = "Cultivar", 
       y = "Vitamin C Content",
       title = "Boxplot of Vitamin C Content by Cultivar")


```
Aside from the outlier in the data in c39 as highlighted in red, the range of the data for c52's vitamin c content is significantly higher than the range for the data of c39's vitamin c content. There is also a wider range of data available for c52 than for c39.


### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
favstats(VitC~Cult, data = veggy)
```
From looking at the data, it can be inferred that the mean, median, and max values of C39 are smaller than the values of mean, median, and max for C52 which indicates a significant gap in the two factors.

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
```{r}
t.test(VitC~Cult, data = veggy)
```
p-value: 0.00000003405. This shows that the data of C39 and C52 differentiate from each other significantly. 

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
The data from the boxplot and the t-test show that the C39 method of cultivation results lower levels of vitamin C within the cabbage represented by veggy, and C52's method of cultivation results in higher levels of vitamin C within the cabbage with a significant difference in the levels of vitamin C between the cabbage cultivated using the two different methods.